Postural developments modulate children's visual access to social information

### 2018-01-31 writeup-cogsci/cogsci2018_faceOnly_alessandro.Rmd
rewording, edits, typos

---
title: "Postural developments mediate children's visual access to social information"
bibliography: xsface.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    \author{{\large \bf Alessandro Sanchez*} \\ \texttt{sanchez7@stanford.edu} \\ Department of Psychology \\ Stanford University
    \And {\large \bf Bria Long*}  \\ \texttt{bria@stanford.edu} \\ Department of Psychology \\ Stanford University
    \And {\large \bf Allison M. Kraus} \\ \texttt{allison.m.kraus@gmail.com} \\ Department of Psychology \\ Stanford University
    \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

abstract: "The ability to process social information--including eye gaze--is a critical component of children's early language and cognitive development. However, as children reach their first birthday, they begin to locomote themselves, walking and exploring their visual environment in an entirely new way. How do these postural and locomotive changes affect children's access to the social information relevant for word-learning? Here, we explore this question by using head-mounted cameras to record infants' (8-16 months of age) egocentric visual perspective and use computer vision algorithms to detect the proportion of faces and wrists in infants' environments. We find that infants' posture and orientation to their caregiver largely mediates their access to social information, suggesting that postural and locomotive developments play a significant role in the emergence of children's linguistic and social capacities. Broadly, we suggest that the combined use of head-mounted cameras and the application of new computer vision techniques is a promising avenue for understanding the statistics of infants' visual and linguistic experience."

@@

```{r, libraries}
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=TRUE, message = FALSE, sanitize = TRUE)
library(readr)
library(dplyr)
library(tidyr)
library(xtable)
library(lubridate)
library(langcog)
library(ggplot2)
library(ggthemes)
library(egg) # plot arranging
library(lme4)
library(gridExtra)
library(feather)
library(assertthat)
```
# Introduction
[^1]: *These authors contributed equally to this work.

[^1] From early infancy, children are deeply engaged in learning from others [@csibra2009natural; @meltzoff2007like]. Even newborns tend to prefer to look at faces with direct vs. averted gaze [@farroni2002eye] and young infants follow overt gaze shifts [@gredeback2010development]. Further, when infants attend to video stimuli, they tend to look mostly at faces at the expense of other visual information -- though older infants start to look towards people's hands and the actions they are performing [@frank2012measuring; @frank2014visual].

Then, however, their view of the world radically changes [@adolph2007]. Infants' motor abilities improve dramatically near the end of the first year of life, allowing them to locomote independently. These motor changes have significant consequences for what children see; crawling and walking infants simply have different views of the world. For example, during spontaneous play in a laboratory playroom, toddlers are more likely to look at the floor while crawling than while walking [@franchak2011]; in general, walking infants tend to have full visual access to their environment and the people in it, while crawling infants do not [@kretch2014].

One possibility is that these motor improvements lead to developmental cascades that impact children’s emerging social, cognitive, and linguistic abilities [@iverson2010]. Indeed, these postural changes also impact how children interact with their mothers; walking (vs. crawling) infants make different kinds of object-related bids for attention from their mothers and tend to hear more action directed statements (e.g., “open it”) [@karasik2014]. Further, in an observational study, @walle2014 found that children who were able to walk had both higher receptive and productive vocabularies. On their account, children’s ability to stand and independently locomote may change their ability to access social information (e.g., faces, gaze)  and in turn to accelerate their own learning.

Recent technological developments allow for testing of this hypothesis by documenting the experiences of infants and children from their own perspective. By using head-mounted cameras, researchers have begun to record the visual experiences of infants and children -- which even for walking children are extremely different from the adult perspective (and not easily predicted by our own adult intuitions) [@clerkin2017;@franchak2011;@yoshida2008]. Children’s views tend to be more restricted and dominated by objects and hands  [@yoshida2008], and computational and empirical work suggest that this restricted viewpoint may be more effective for learning objects and their labels than the comparable adult perspective [@bambach2017;@yurovsky2012]. This perspective changes over the first two years of life, as views transition from primarily containing close up views of faces to capturing views of hands paired with the objects they are acting on [@fausey2016].

Here, we directly examine whether postural and locomotive developments change the availability of social information--the presence of faces and hands. To do so, we recorded the visual experience of a group of infants in three age ranges (8,12, and 16 months) using head-mounted cameras during a brief laboratory free-play session; children’s posture and orientation relative to their caregiver were also recorded from a third-person perspective and hand-annotated. We then capitalize on recent improvements in face and pose detection algorithms [@zhang2016; @cao2017realtime] to analyze the frequencies of faces and hands (using wrists as a proxy for the latter) in the child’s visual environment, both overall and relative to naming events by their caregivers. We hypothesized that there would be differential access to social information based on children's postural developments: crawling infants would see fewer faces because they would primarily be looking at the ground, while walking toddlers would have access to a richer visual landscape, thus rendering accessible a larger portion of the social information in their environment.

@@

Even with the fish-eye lens, the vertical field of view of the camera is still considerably reduced compared to the child's approximate vertical field of view, which spans around 100--120$^{\circ}$ in the vertical dimension by 6-7 months of age [@mayer1988;@cummings1988]. As we were primarily interested in the presence of faces in the child's field of view, we chose to orient the camera upwards to capture the entirety of the child's upper visual field where the child is likely to see adult faces, understanding that this decision limited our ability to detect hands (especially those of the child, which are typically found at the bottom of the visual field)

### Procedure
All parents signed consent documents while children were fitted with the headcam. If the child was uninterested in wearing the headcam or tried to take it off, the experimenter presented engaging toys to try to draw the child's focus away from the headcam. When the child was comfortable wearing the headcam, the child and caregiver were shown to a playroom for the free-play session. Parents were shown a box containing three pairs of novel and familiar objects (e.g., a ball and a microfiber duster, named a "zem"), and were instructed to play with the object pairs with their child one at a time, "as they typically would." All parents confirmed that their child had not previously seen the novel toys and were instructed to use the novel labels to refer to the novel toys. The experimenter then left the playroom for approximately 15 minutes, during which a tripod-mounted camera in the corner of the room recorded the session and the headcam captured video from the child's perspective.

### Data Processing and Annotation
Headcam videos were trimmed such that they excluded the instruction phase when the experimenter was in the room and were automatically synchronized with the tripod-mounted videos using FinalCut Pro Software. These sessions yielded videos of 
`r round(sum(inc_subs$len.min), digits = 0)` minutes (almost a milion frames), with an average video length of
`r round(sum(inc_subs$len.min)/60, digits = 2)` minutes
(min = `r round(min(inc_subs$len.min), digits = 2)`, max = `r round(max(inc_subs$len.min), digits = 2)`).

@@

## Face and Hand Detection
We used three face detection systems to measure infants' access to faces. The first of these is the most commonly-used and widely available face detection algorithm: Viola-Jones. We used this algorithm as a benchmark for performance, as while it can achieve impressive accuracy in some situations, it is notoriously bad at dealing with occluded faces [@scheirer2014perceptual]. We next tested the performance of two face detectors that both made use of recently developed Convolutional Neural Networks (CNNs) to extract face information. The first algorithm was specifically optimized for face detection, and the second algorithm was optimized to extract information about the position of 18 different body parts. For the second algorithm [OpenPose, @cao2017realtime], we used the agent's nose (one of the body parts detected) to operationalize the presence of faces, as any half of a face necessarily contains a nose.

The OpenPose detector also provided us with the location of an agent's wrists, which we used as a proxy for hands for two reasons. First, as we did not capture childrens entire visual field. the presence of a wrist is likely often indicative of the presence of a hand within the field of view. Second, hands are often occluded by objects when caregivers are interacting with children, yet still visually accessible by the child and part of their joint interaction. 
\begin{figure*}
\centering
\includegraphics[width=5.5in]{images/detector_samples_banner.pdf}
\caption{\label{fig:frames} Example face and pose detections made by OpenPose (top row) and MTCNN (bottom row) from a child in each age group. The last column features a false positive from OpenPose and a false negative from MTCNN.}
\end{figure*}

@@

The CNN-based pose detector  [OpenPose, @cao2017realtime; @simon2017hand; @wei2016cpm]) provided the locations of 18 body parts (ears, nose, wrists, etc.) and is available at https://github.com/CMU-Perceptual-Computing-Lab/openpose. The system uses a CNN for initial anatomical detection and subsequently applies part affinity fields (PAFs) for part association, producing a series of body part candidates. The candidates are then matched to a single individual and finally assembled into a pose; here, we only made use of the body parts relevant to the face and hands (nose and wrists). We operationalized face detections as any frames containing a nose, and hand detections as any frames containing either the left or right wrist.

### Detector evaluation
To evaluate face detector performance, we hand-labeled  an "gold set" of labeled frames. To account for the relatively rare appearance of faces in the dataset, we  hand abeled two types of samples: a sample containing a high density of faces (half reported by MTCNN, half by OpenPose) and a random sample from the remaining frames. Each sample was comprised of an equal number of frames taken from each child's video. For wrist detections, the "gold set" was constructed in the same manner, except frames with a high density of wrists came only from detections made by OpenPose.  Faces were classified as present if at least half of the face was showing; wrists were classified as present if any part of the wrist was showing.  Precision (hits / hits + false alarms), recall (hits / hits + misses), and F-score (harmonic mean of precision and recall) were calculated for all detectors and are reported in Table 2.

@@

```{r posture, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=3.5, fig.height=3.5, fig.cap = "Proportion time that infants in each age group spent in each posture/orientation relative to their caregiver." }
p1=ggplot(posture, aes(x = factor(age.grp), y = prop.time, col = posture)) + 
  geom_boxplot() + 
  ylab("Proportion Time") + 
  xlab("") + 
  theme_few() +
  scale_x_discrete( labels=c("8 m.", "12 m.", "16 m."))

@@

ggarrange(p1,p2)
```
## Changes in Posture and Orientation
The proportion of time infants spent sitting decreased with age, and the proportion of time infants spent standing increased with age. Both 8 month-olds and 12 month-olds spent equivalent amounts of time lying/crawling, which was markedly decreased in the 16-month-olds, who spent most of their time sitting or standing (see Figure \ref{fig:posture}).  We also observed changes in children's orientation relative to their caregivers: the 8-month-olds spent more time with their caregiver behind them supporting their sitting positions (see Figure \ref{fig:posture}).

## Changes in Access to Faces and Hands
We examined the proportion of face and wrist detections across age (see Figure \ref{fig:detByAge}). We observed a slight U-shaped function in face detections, such that 12-month-olds appeared to have visual acces to slightly fewer faces faces than 8 or 16-month-olds; conversely, wrist detections perhaps appeared to generally increase with age.

Age related effects were much smaller than postural and locomotive changes on children's visual access to faces and wrists/hands. Children's posture was a major factor both in how many faces and wrists/hands they saw during the play session. Infants who were sitting saw more faces than infants who were lying down or being carried, while infants who were standing saw the most faces (Figure \ref{fig:detByPosOrient}, upper panel); this same pattern was also true for wrists/hand detections. Children’s orientation also impacted their visual access to faces and hands: children who were far away from their caregiver were more likely to see faces/hands than children who were close to their caregiver (Figure \ref{fig:detByPosOrient}, lower panel).

@@

```{r detByPosOrient, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion face and wrist detections as a function of children's posture (top panel) and orientation (bottom panel), binned by the age of the participant."}

@@

A summary of the coefficients of a models can be found in Table 2.  While infant's posture and orientation significantly impacted the proportion of faces and hands that infants saw, age was not a significant predictor in either model. Thus, these results suggest that infants' visual access to social information is mediated by their posture and orientation, which is in turn a function of their general locomotor development.

@@

Finally, we explored how face and wrist detections changed during object labeling events as a function of infant's posture and orientation. We analyzed a four-second window around each labeling event (e.g., "Look at the [zem]!"); these labeling events were hand-annotated and synchronized with the frame-by-frame face/wrist detections.  We found that infants' posture and orientations mediated their visual access to faces and wrists/hands during labeling events; infants who were sitting or standing were more likely to have visual access to this social information (see Figure \ref{fig:detByNaming}). However, we did not find that infants saw particularily more faces or wrists/hands during naming events relative to baseline (avg. difference in proportion of wrists, 8 m.o. = `r round(wrists_naming$avgBaselineDiff[1],3)`, 12 m.o. = `r round(wrists_naming$avgBaselineDiff[2],3)`, 16 m.o. = `r round(wrists_naming$avgBaselineDiff[3],3)`;  avg. difference in proportion of faces, 8 m.o. = `r round(faces_naming$avgBaselineDiff[1],3)`, 12 m.o. = `r round(faces_naming$avgBaselineDiff[2],3)`, 16 m.o. = `r round(faces_naming$avgBaselineDiff[3],3)`).

@@

We used a head-mounted camera to explore how children's postural and locomotor development affects their visual access to social information, here operationalized as the presence of the faces and hands of their caregiver. Children's posture and orientation towards their caregiver changed systematically across age, and both of these factors influenced the proportion of faces and hands that were available in the child's visual field. This work suggests that motor development mediates how infants experience their visual world and the social information in it: Infants that are sitting and standing have a different view of their world, the people in it, and the actions that are being performed.

```{r detByNaming, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=3, fig.height=3, fig.cap = "Proportion face and wrist detections around a naming instance ('Look, a Zem'; +/- 2 seconds around each utterance) as a function of infants' posture. Error bars represent non-parametric bootstrapped 95 percent confidence intervals."}

>>>>

---
title: "Postural developments modulate children's visual access to social information"
bibliography: xsface.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    \author{{\large \bf Alessandro Sanchez\thanks{These authors contributed equally to this work.}} \\ \texttt{sanchez7@stanford.edu} \\ Department of Psychology \\ Stanford University
    \And {\large \bf Bria Long\footnotemark[1]}  \\ \texttt{bria@stanford.edu} \\ Department of Psychology \\ Stanford University
    \And {\large \bf Allison M. Kraus} \\ \texttt{allison.m.kraus@gmail.com} \\ Department of Psychology \\ Stanford University
    \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

abstract: "The ability to process social information is a critical component of children's early language and cognitive development. However, as children reach their first birthday, they begin to locomote themselves, dramatically affecting their visual access to this information. How do these postural and locomotive changes affect children's access to the social information relevant for word-learning? Here, we explore this question by using head-mounted cameras to record 36 infants' (8-16 months of age) egocentric visual perspective and use computer vision algorithms to estimate the proportion of faces and hands in infants' environments. We find that infants' posture and orientation to their caregiver modulates their access to social information, confirming previous work that suggests motoric developments play a significant role in shaping the input to children's developing linguistic and social capacities. We suggest that the combined use of head-mounted cameras and the application of new computer vision techniques is a promising avenue for understanding the statistics of infants' visual and linguistic experience."

@@

```{r, libraries}
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=TRUE, message = FALSE, sanitize = TRUE)
library(readr)
library(dplyr)
library(tidyr)
library(xtable)
library(lubridate)
library(langcog)
library(ggplot2)
library(ggthemes)
library(egg) # plot arranging
library(lme4)
library(gridExtra)
library(feather)
library(assertthat)
```
# Introduction
[^1]: These authors contributed equally to this work.

From early infancy, children are deeply engaged in learning from others [@csibra2009natural; @meltzoff2007like]. Even newborns tend to prefer to look at faces with direct vs. averted gaze [@farroni2002eye] and young infants follow overt gaze shifts [@gredeback2010development]. Further, when infants attend to video stimuli, they tend to look mostly at faces at the expense of other visual information -- though older infants start to look towards people's hands and the actions they are performing [@frank2012measuring; @frank2014visual].

Then, however, their view of the world radically changes [@adolph2007]. Infants' motor abilities improve dramatically near the end of the first year of life, allowing them to locomote independently. These motor changes have significant consequences for what children see; crawling and walking infants simply have different views of the world. For example, during spontaneous play in a laboratory playroom, toddlers are more likely to look at the floor while crawling than while walking [@franchak2011]. In general, walking infants tend to have full visual access to their environment and the people in it, while crawling infants do not [@kretch2014].

One possibility is that these motor improvements lead to developmental cascades that impact children’s emerging social, cognitive, and linguistic abilities [@iverson2010]. These postural changes also impact how children interact with their mothers: walking (vs. crawling) infants make different kinds of object-related bids for attention from their mothers and tend to hear more action directed statements (e.g., “open it”) [@karasik2014]. Further, in an observational study, @walle2014 found that children who were able to walk had both higher receptive and productive vocabularies. On their account, children’s ability to stand and independently locomote may change their ability to access social information (e.g., faces, gaze)  and in turn to accelerate their own learning.

Recent technological developments allow for testing of this hypothesis by documenting the experiences of infants and children from their own perspective. By using head-mounted cameras, researchers have begun to record the visual experiences of infants and children -- which even for walking children are extremely different from the adult perspective (and not easily predicted by our own adult intuitions) [@clerkin2017;@franchak2011;@yoshida2008]. Children’s views tend to be more restricted and dominated by objects and hands  [@yoshida2008], and computational and empirical work suggest that this restricted viewpoint may be more effective for learning objects and their labels than the comparable adult perspective [@bambach2017;@yurovsky2012]. This perspective changes over the first two years of life, as views transition from primarily containing close up views of faces to capturing views of hands paired with the objects they are acting on [@fausey2016]. These changes may be driven by – or independent from – the concurrent motoric changes described above.

Here, we directly examine whether postural and locomotive developments change the availability of social information -- the presence of faces and hands. To do so, we recorded the visual experience of a group of infants in three age ranges (8,12, and 16 months) using head-mounted cameras during a brief laboratory free-play session; children’s posture and orientation relative to their caregiver were also recorded from a third-person perspective and hand-annotated. We then capitalize on recent improvements in face and pose detection algorithms [@zhang2016; @cao2017realtime] to analyze the frequencies of faces and hands (using wrists as a proxy for the latter) in the child’s visual environment, both overall and relative to naming events by their caregivers. We hypothesized that there would be differential access to social information based on children's postural developments: crawling infants would see fewer faces because they would primarily be looking at the ground, while walking toddlers would have access to a richer visual landscape, thus providing children with greater access to the social information in their environment.

@@

Even with the fish-eye lens, the vertical field of view of the camera is still considerably reduced compared to the child's field of view, which spans around 100--120$^{\circ}$ in the vertical dimension by 6-7 months of age [@mayer1988;@cummings1988]. As we were primarily interested in the presence of faces in the child's field of view, we chose to orient the camera upwards to capture the entirety of the child's upper visual field where the child is likely to see adult faces, understanding that this decision limited our ability to detect hands (especially those of the child, which are typically found at the bottom of the visual field).

### Procedure
All parents signed consent documents while children were fitted with the headcam. If the child was uninterested in wearing the headcam or tried to take it off, the experimenter presented engaging toys to try to draw the child's focus away from the headcam. When the child was comfortable wearing the headcam, the child and caregiver were shown to a playroom for the free-play session. Parents were shown a box containing three pairs of novel and familiar objects (e.g., a ball and a microfiber duster, named a "zem"), and were instructed to play with the object pairs with their child one at a time, "as they typically would." All parents confirmed that their child had not previously seen the novel toys and were instructed to use the novel labels to refer to the toys. The experimenter then left the playroom for approximately 15 minutes, during which a tripod-mounted camera in the corner of the room recorded the session and the headcam captured video from the child's perspective.

### Data Processing and Annotation
Headcam videos were trimmed such that they excluded the instruction phase when the experimenter was in the room and were automatically synchronized with the tripod-mounted videos using FinalCut Pro Software. These sessions yielded videos of 
`r round(sum(inc_subs$len.min), digits = 0)` minutes (almost a million frames), with an average video length of
`r round(sum(inc_subs$len.min)/60, digits = 2)` minutes
(min = `r round(min(inc_subs$len.min), digits = 2)`, max = `r round(max(inc_subs$len.min), digits = 2)`).

@@

## Face and Hand Detection
We used three face detection systems to measure infants' access to faces. The first of these is the most commonly-used and widely available face detection algorithm: Viola-Jones. We used this algorithm as a benchmark for performance, as while it can achieve impressive accuracy in some situations, it is notoriously bad at dealing with occluded faces [@scheirer2014perceptual]. We next tested the performance of two face detectors that both made use of recently developed Convolutional Neural Networks (CNNs) to extract face information. The first algorithm was specifically optimized for face detection, and the second algorithm was optimized to extract information about the position of 18 different body parts. For the second algorithm [OpenPose; @cao2017realtime], we used the agent's nose (one of the body parts detected) to operationalize the presence of faces, as any half of a face necessarily contains a nose.

The OpenPose detector also provided us with the location of an agent's wrists, which we used as a proxy for hands for two reasons. First, as we did not capture children's entire visual field, the presence of a wrist is likely often indicative of the presence of a hand within the field of view. Second, hands are often occluded by objects when caregivers are interacting with children, yet still visually accessible by the child and part of their joint interaction. 
\begin{figure*}
\centering
\includegraphics[width=5.5in]{images/detector_samples_banner.pdf}
\caption{\label{fig:frames} Example face and pose detections made by OpenPose (top row) and MTCNN (bottom row) from a child in each age group. The last column features a false positive from OpenPose and a false negative from MTCNN.}
\end{figure*}

@@

The CNN-based pose detector  [OpenPose; @cao2017realtime; @simon2017hand; @wei2016cpm]) provided the locations of 18 body parts (ears, nose, wrists, etc.) and is available at https://github.com/CMU-Perceptual-Computing-Lab/openpose. The system uses a CNN for initial anatomical detection and subsequently applies part affinity fields (PAFs) for part association, producing a series of body part candidates. The candidates are then matched to a single individual and finally assembled into a pose; here, we only made use of the body parts relevant to the face and hands (nose and wrists).

### Detector evaluation
To evaluate face detector performance, we hand-labeled a "gold set" of labeled frames. To account for the relatively rare appearance of faces in the dataset, we hand-labeled two types of samples: a sample containing a high density of faces (half reported by MTCNN, half by OpenPose) and a random sample from the remaining frames. Each sample was comprised of an equal number of frames taken from each child's video. For wrist detections, the "gold set" was constructed in the same manner, except frames with a high density of wrists came only from detections made by OpenPose.  Faces were classified as present if at least half of the face was showing; wrists were classified as present if any part of the wrist was showing.  Precision (hits / hits + false alarms), recall (hits / hits + misses), and F-score (harmonic mean of precision and recall) were calculated for all detectors and are reported in Table 2.

@@

```{r posture, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=3.5, fig.height=3.5, fig.cap = "Proportion of time that infants in each age group spent in each posture/orientation relative to their caregiver." }
p1=ggplot(posture, aes(x = factor(age.grp), y = prop.time, col = posture)) + 
  geom_boxplot() + 
  ylab("Proportion Time") + 
  xlab("") + 
  theme_few() +
  scale_x_discrete( labels=c("8 m.", "12 m.", "16 m."))

@@

ggarrange(p1,p2)
```
## Changes in Posture and Orientation
The proportion of time infants spent sitting decreased with age, and the proportion of time infants spent standing increased with age. Both 8-month-olds and 12-month-olds spent equivalent amounts of time lying/crawling, which was markedly decreased in the 16-month-olds, who spent most of their time sitting or standing (see Figure \ref{fig:posture}).  We also observed changes in children's orientation relative to their caregivers: the 8-month-olds spent more time with their caregiver behind them supporting their sitting positions (see Figure \ref{fig:posture}).

## Changes in Access to Faces and Hands
We examined the proportion of face and hand detections across age (see Figure \ref{fig:detByAge}). We observed a slight U-shaped function in face detections, such that 12-month-olds appeared to have visual access to slightly fewer faces faces than 8 or 16-month-olds; conversely, hand detections perhaps appeared to generally increase with age.

Age related effects were much smaller than postural and locomotive changes on children's visual access to faces and hands. Children's posture was a major factor both in how many faces and hands they saw during the play session. Infants who were sitting saw more faces than infants who were lying down or being carried, while infants who were standing saw the most faces (Figure \ref{fig:detByPosOrient}, upper panel); this same pattern was also true for hand detections. Children’s orientation also impacted their visual access to faces and hands: children who were far away from their caregiver were more likely to see faces/hands than children who were close to their caregiver (Figure \ref{fig:detByPosOrient}, lower panel).

@@

```{r detByPosOrient, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of face and wrist detections as a function of children's posture (top panel) and orientation (bottom panel), binned by the age of the participant."}

@@

A summary of the coefficients of the models can be found in Table 2.  While infant's posture and orientation significantly impacted the proportion of faces and hands that infants saw, age was not a significant predictor in either model. Thus, these results suggest that infants' visual access to social information is modulated by their posture and orientation, which is in turn a function of their general locomotor development.

@@

Finally, we explored how face and hand detections changed during object labeling events as a function of infants' posture and orientation. We analyzed a four-second window around each labeling event (e.g., "Look at the [zem]!"); these labeling events were hand-annotated and synchronized with the frame-by-frame face/hand detections.  We found that infants' posture and orientations modulated their visual access to faces and hands during labeling events; infants who were sitting or standing were more likely to have visual access to this social information (see Figure \ref{fig:detByNaming}). However, we did not find that infants saw particularly more faces or hands during naming events relative to baseline (avg. difference in proportion of hands, 8 m.o. = `r round(wrists_naming$avgBaselineDiff[1],3)`, 12 m.o. = `r round(wrists_naming$avgBaselineDiff[2],3)`, 16 m.o. = `r round(wrists_naming$avgBaselineDiff[3],3)`;  avg. difference in proportion of faces, 8 m.o. = `r round(faces_naming$avgBaselineDiff[1],3)`, 12 m.o. = `r round(faces_naming$avgBaselineDiff[2],3)`, 16 m.o. = `r round(faces_naming$avgBaselineDiff[3],3)`).

@@

We used a head-mounted camera to explore how children's postural and locomotor development affects their visual access to social information, here operationalized as the presence of the faces and hands of their caregiver. Children's posture and orientation towards their caregiver changed systematically across age, and both of these factors influenced the proportion of faces and hands that were available in the child's visual field. This work suggests that motor development modulates how infants experience their visual world and the social information in it: Infants that are sitting and standing have a different view of their world, the people in it, and the actions that are being performed.

```{r detByNaming, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=3, fig.height=3, fig.cap = "Proportion of face and hand detections around a naming instance ('Look, a Zem'; +/- 2 seconds around each utterance) as a function of infants' posture. Error bars represent non-parametric bootstrapped 95 percent confidence intervals."}
